Report

### 2021-05-27 paper/manuscript.Rmd
Add spatial analysis and results

```{r}
loadd(com_analysis_data)
```

@@

We characterized the temporal trajectories of network and community structure at
each site. We used a method based on second order polynomial which allows to
assess both the direction and the monotony of temporal trends
[@rigal_method_2020].

- Why do we want to classify temporal trends?
- How do we select station for each variable?

@@

# Result

Overall, we found no significant effect of the temporal gain or losses of total
biomass and species richness on the relationship between the temporal trends of
community structure and that of biomass and species richness (slope X, Table X).

## Community structure and biomass

We found a significant positive relationship between the temporal trends of total biomass from
one side and species richness, average trophic level, connectance from the other
side (slopes XX, Figure X, Table X), meaning that they increased in time when
the total biomass increased in time and respectively that they decreased in time
when the total biomass decreased in time.

We found that a significant negative relationship between the temporal trends of
total biomass and that of the pielou of biomass (slopes XX, Figure X, Table X),
meaning that the pielou value increased in time when the total biomass decreased in time and
respectively that the pielou value decreased in time when the total biomass
increase in time. However, we found no relationship between the temporal trends of
total biomass and that of the pielou of individual.

## Community structure and species richness

The temporal trends of total biomass, average trophic level, pielou of biomass,
pielou of individual had a positive relationship with that of species
richness (slopes XX, Figure X, Table X). However, the direct relationship
between the temporal trends of average trophic level and the one of species
richness was not significant after controling for total biomass temporal trends.

@@

```{r}
loadd(p_fig1_2)
p_fig1_2
```

>>>>

```{r}
loadd(com_analysis_data, full_data2)
```
```{r}
nb_st <- unique(full_data2$station) %>% length
```

@@

With the goal to characterize the links among the temporal variations of network
and community structure and the temporal variations of community biomass and
species richness, we characterized the temporal trajectories of network and
community structure at each site. We used a method based on second order
polynomial which allows to assess both the direction and the monotony of
temporal trends [@rigal_method_2020]. To avoid complex variations of biomass and
species richness, we selected the stations that displayed monotonic trends for
theses variable. Over the `r nb_st` stations, the selection procedure resulted
in XX stations for biomass and species richness analysis.

@@

We selected the same stations that was used for the temporal analysis.

# Statistical analysis

## Temporal trends

With the aim to test (1) the relationship among the temporal dynamics of network
structure from one side and species richness and community biomass from another
side, (2) if those relationships were different if the communities were
assembling or disassembling, (3) if those relationships were different if
small/big communities, we modelled the dynamics the temporal trends of food-web
structure ($dN$) in function of the temporal trends of community biomass ($dB$) and species
richness ($dR$), if the latter was positive of not (Inc) and with respectively the median
community biomass ($B_i$) and species richness ($R_i$)of the three first years of the temporal
series .

$dN = dB + B_i + dB \times B + Inc \times B_i + dB \times Inc \times B_i$

$dN = dR + R_i + dR \times R_i + Inc \times R_i + dR \times Inc \times R_i$

With:

  - $dN$: temporal trend of network structure and communities structure
  - $dB$: temporal trend of community (log) biomass
  - $dR$: temporal trend of (log) species richness 
  - $B_i$: median community biomass of the first three year
  - $R_i$: median species richness of the first three year
  - $Inc$: Is $dB > 0$?

## Spatial trends

Spatial gradient of food-web structure are partly driven by environmental gradients, so
we controlled relationships among community structure variables by two PCA axis
synthesizing respectively (1) stream size and (2) average temperature and
enrichment. Enrichment was characterized by the average Biological Oxygen
Demand [BOD, @mallin_factors_2006].

$N =  B + R + E_1 + E_2 $

With:

  - $N$: median network structure and communities structure
  - $B$: median community biomass
  - $R$: median species richness

# Results

```{r}
loadd(rsq_sp_mod, summary_table, sp_models, model_summary)
rsq <- summary_table %>%
  filter(y %in% get_com_str_var(all = FALSE), x %in% c("log_bm_std",
      "log_rich_std")) %>%
select(y, x, mod_summary_table) %>%
unnest(mod_summary_table) %>%
select(y, x, r.squared, adj.r.squared)
```

```{r}
rsq_nind_bm <- rsq[rsq$y == "piel_nind" & rsq$x == "log_bm_std",]$adj.r.squared %>%
  round(., 3)
rsq_bm_rich <- rsq[rsq$y == "log_bm_std" & rsq$x == "log_rich_std",]$adj.r.squared %>%
  round(., 3)
rsq_tlvl_rich_sp <- rsq_sp_mod$log_rich_std[
  rsq_sp_mod$log_rich_std$Response == "w_trph_lvl_avg", 
  ]$Conditional %>%
    round(., 3)
rsq_piel_bm_rich_sp <- rsq_sp_mod$log_bm_std[
  rsq_sp_mod$log_rich_std$Response == "piel_bm", 
  ]$Conditional %>%
    round(., 3)
```

Overall, we found high heterogeneity in the explicative power of statistical
models linking temporal dynamics of food-web structure and the one of community biomass and species richness spanning from $R_{adj}^2= `r rsq_nind_bm`$ for
the relationships between to $R_{adj}^2= `r rsq_bm_rich`$ between biomass and
species richness (Table \@ref(tab:rsq)). The spatial relationships among
food-web structure aspects were more performant, with $R_{cond}^2$ varing from 
`r rsq_tlvl_rich_sp` to `r rsq_piel_bm_rich_sp` (Table \@ref(tab:rsq-sp)).

Overall, we found no significant effect of the temporal gain or losses of
communinity biomass biomass and species richness on the relationship between the
temporal trends of community structure and that of biomass and species richness
(Table \@ref(tab:aov-bm), \@ref(tab:aov-rich)).

## Relationships between temporal trends

### Food-web structure and biomass

```{r}
loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
reg_bm <- model_log_bm_f3y_table_medium$reg_table
#reg_bm[reg_bm$y == ]
```
We found a significant positive relationship between the temporal trends of total biomass from
one side and species richness, average trophic level, connectance from the other
side (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)), meaning that they increased in time when
the total biomass increased in time and respectively that they decreased in time
when the total biomass decreased in time.

We found that a significant negative relationship between the temporal trends of
total biomass and that of the pielou of biomass (slopes XX, Figure X, Table X),
meaning that the eveness of biomass across species increased in time when the
total biomass decreased in time and respectively that the evenness decreased
in time when the total biomass increase in time (Fig. \@ref(fig:bm), Table
\@ref(tab:aov-bm)). However, we found no relationship between the temporal
trends of total biomass and that of the pielou
of individual.

### Community structure and species richness

The temporal trends of total biomass, average trophic level, pielou of biomass,
pielou of individual had a positive relationship with that of species richness
(Fig. \@ref(fig:rich), Table \@ref(tab:aov-rich)). However, the direct
relationship between the temporal trends of average trophic level and the one of
species richness was not significant after controling for total biomass temporal
trends.

@@

```{r}
loadd(p_fig1_2, sp_relation_plot2, predict_plot2)
theme_set(theme_cowplot())
p_bm <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE,
  bm_x = "bm_std", rich_x = "rich_std"
  )$bm
plot_grid(plotlist = p_bm)

sp_bm <- sp_relation_plot2 %>%
  filter(x == "bm_std")
p_sp_bm <- sp_bm$gg 
names(p_sp_bm) <- sp_bm$y

reorder_p_sp_bm <- p_sp_bm
reorder_p_sp_bm[[1]] <- p_sp_bm$ct_ff 
reorder_p_sp_bm[[2]] <- p_sp_bm$w_trph_lvl_avg 
reorder_p_sp_bm[[3]] <- p_sp_bm$piel_nind 
reorder_p_sp_bm[[4]] <- p_sp_bm$piel_bm 
reorder_p_sp_bm[[5]] <- p_sp_bm$log_rich_std 
```

```{r}
fig1_left <- plot_grid(plotlist = p_bm, ncol = 1)
fig1_right <- plot_grid(plotlist = p_sp_bm, ncol = 1)
#plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)

ti <- list()
for (i in 1:5) {
  ti[[i]] <- list(p_bm[[i]], reorder_p_sp_bm[[i]]) 
}

```

```{r bm, fig.height = 12}
# Make the label on two lines 
top <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
fig1 <- plot_grid(top, p_bm[[6]], ncol = 1, rel_heights = c(1, .1)) 
fig1
```

```{r}
p_rich <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE)$rich
#plot_grid(plotlist = p_rich)

sp_rich <- sp_relation_plot2 %>%
  filter(x == "log_rich_std")
p_sp_rich <- sp_rich$gg
names(p_sp_rich) <- sp_rich$y

reorder_p_sp_rich <- p_sp_rich
reorder_p_sp_rich[[1]] <- p_sp_rich$ct_ff 
reorder_p_sp_rich[[2]] <- p_sp_rich$w_trph_lvl_avg 
reorder_p_sp_rich[[3]] <- p_sp_rich$piel_nind 
reorder_p_sp_rich[[4]] <- p_sp_rich$piel_bm 
reorder_p_sp_rich[[5]] <- p_sp_rich$log_bm_std

```

```{r}
fig2_left <- plot_grid(plotlist = p_rich, ncol = 1)
fig2_right <- plot_grid(plotlist = p_sp_rich, ncol = 1)
#plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)

trich <- list()
for (i in 1:5) {
  trich[[i]] <- list(p_rich[[i]], reorder_p_sp_rich[[i]]) 
}
```

```{r rich, fig.height = 12}
# Make the label on two lines 
top_rich <- plot_grid(plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]), ncol = 2)
fig2 <- plot_grid(top_rich, p_rich[[6]], ncol = 1, rel_heights = c(1, .1))
fig2
```

```{r}
```

# Tables

## Statistical models

### Temporal

```{r}
loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
```

```{r}
model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% get_com_str_var(all = FALSE)) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of 
      community biomass and the temporal trends of the network structure."
    ),
  label = "tab:aov-bm"

  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% get_com_str_var(all = FALSE)) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of species
      richness and the temporal trends of the network structure."
    ),
  label = "tab:aov-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_bm_f3y_table_medium$reg_table %>% 
  filter(y %in% get_com_str_var(all = FALSE)) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of community biomass and the temporal trends
      of the network structure."),
  label = "tab:reg-bm"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium$reg_table %>% 
  filter(y %in% get_com_str_var(all = FALSE)) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of species richness and the temporal trends of
      the network structure."
    ),
  label = "tab:reg-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
rsq %>%
  rename(
    Response = y, Explicative = x, 
    `Squared R` = r.squared, `Adjusted squared R` = adj.r.squared
  ) %>% 
  select(Explicative, Response, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Squared and adjusted squared R for linear models of spatial relationships."),
  label = "tab:rsq"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

### Spatial

```{r}
loadd(tab_sp_anova)
```

```{r}
tab_sp_anova$log_bm_std %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the spatial variation of community
      biomass and the one of network structure."),
  label = "tab:aov-bm-sp"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
tab_sp_anova$log_rich_std %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the spatial variation of species
      richness and the one of network structure."),
  label = "tab:aov-rich-sp"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}

table_rsq_sp <- map2(rsq_sp_mod, names(rsq_sp_mod),
  ~mutate(.x, Explicative = .y) %>%
    select(Explicative, Response, Marginal, Conditional)
) %>%
do.call(rbind, .)

table_rsq_sp %>%
  mutate(
    Explicative = str_replace_all(Explicative, var_replacement()),
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Marginal and conditional squared R for spatial models."),
  label = "tab:rsq-sp"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")

```

### 2021-05-27 report_rdv.Rmd
Add spatial analysis and results

```{r}
loadd(sp_relation_plot)
plot_grid(plotlist = sp_relation_plot$gg)

@@

>>>>

```{r}
loadd(sp_relation_plot2)
plot_grid(plotlist = sp_relation_plot$gg)

@@

## Connectance and biomass

```{r}

loadd(est_sp_models, colin_sp_models, sp_models)
loadd(data4model, sp_st_data, summary_var_med)
data4model[1, ]$data_model[[1]]

est_sp_models$log_bm_std$ct_ff
colin_sp_models$log_bm_std$ct_ff
cf_bm_sp_mod <- sp_models$log_bm_std$ct_ff
```

On ne trouve pas d'effet de la biomasse sur la connectance, à part quand on la
controle pour la richness. Ce qui se comprend car la richness a un effet très
fort sur la connectance, qui enlève du coup beaucoup de variabilité.

```{r}
test_sp_model <- get_mod_list(.data = as.data.frame(sp_st_data))
est_sp_models = map(test_sp_model, broom.mixed::tidy)
```
```{r}
test_mod <- lm(ct_ff ~ log_RC1 + log_RC2 + log_bm_std, as.data.frame(sp_st_data))
test_mod_rich <- lm(ct_ff ~ log_RC1 + log_RC2 + log_bm_std + log_rich_std, as.data.frame(sp_st_data))
```

##

##

```{r}
loadd(sp_models, anova_table_sp, tab_sp_anova)
